Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-02-10 manuscript/supplements_rsfmri.Rmd
missing model in supplement and typos

### Aggregated DMN for two timepoints, adjusted for age and sex (Model 1a)
```{r calc DMN two tp, age and sex,results = 'asis', echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tp=anova(R1,R0)
```

@@

>>>>

### Aggregated DMN for two timepoints, adjusted for age and sex (Model 1a)
```{r calc DMN two tp, age and sex,results = 'asis', echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tp=anova(R1,R0)
```

@@

### Reward network
#### Model 2a and 2b (adjusting for mFD)
```{r "reward model, mean, change BMI", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~  mean.BMI + within.BMI + Age_BL + Sex  + (1|subj.ID), data=final_FC)
R01 = lme4::lmer(mean_Rew_conn ~ mean.BMI +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R02 = lme4::lmer(mean_Rew_conn ~ within.BMI +  Age_BL + Sex +(1|subj.ID), data=final_FC)
anvwithinBMI=anova(R1,R01)
anvmeanBMI=anova(R1,R02)
p_meanBMI=anvmeanBMI$`Pr(>Chisq)`[2]

R11 = lme4::lmer(mean_Rew_conn ~  mean.BMI + within.BMI + Age_BL + Sex + logmFD + (1|subj.ID), data=final_FC)
R12a = lme4::lmer(mean_Rew_conn ~ within.BMI +  Age_BL + Sex + logmFD+(1|subj.ID), data=final_FC)
anvmeanBMI_adjmFD=anova(R11,R12a)
```

```{r reward model_BMIFD results, caption="Model 2a and 2b for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R1, R11),
  custom.coef.names = c("Intercept", "average BMI", "change BMI", "Age", "Sex", "logmFD"),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```
#### Model 2c (adjusting for average and change in mFD)
```{r "reward model mean+change of BMI+logmFD", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~  mean.BMI + within.BMI + mean.logmFD + within.logmFD + Age_BL + Sex  + (1|subj.ID), data=final_FC)
R01 = lme4::lmer(mean_Rew_conn ~ mean.BMI + mean.logmFD + within.logmFD + Age_BL + Sex +(1|subj.ID), data=final_FC)
R02 = lme4::lmer(mean_Rew_conn ~ within.BMI + mean.logmFD + within.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R03 = lme4::lmer(mean_Rew_conn ~ mean.BMI  + within.BMI +  within.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R03 = lme4::lmer(mean_Rew_conn ~ mean.BMI  + within.BMI +  mean.logmFD +  Age_BL + Sex +(1|subj.ID), data=final_FC)
anvwithinBMI=anova(R1,R01)
anvmeanBMI=anova(R1,R02)
anvmeanFD=anova(R1,R03)
anvwithinFD=anova(R1,R03)

```{r reward_BMI_splitFD results, caption="Model 2c for aggregated DMN FC", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R1), custom.coef.names=c("Intercept", "average BMI", "change BMI", "average mFD", "change mFD", "Age", "Sex"), custom.model.names = "R1", float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
